\vskip-0.6in LOBBYING AND LEGISLATIVE UNCERTAINTY

### 2016-02-18 draft.tex
proofread sec:two

The Lagrangian for the problem is the same as Expression~\ref{eq:objb}, with the addition of three terms for the non-negativity constraints: $\lambda_X b_0 + \lambda_Y b_{-\frac{1}{2}} + \lambda_Z b_{\frac{1}{2}}$. Thus the full set of first order conditions are
\[
    W_B\frac{e^{-X}}{\left(1+e^{-X}\right)^2}\left[\frac{e^{-Z} + e^{-Y}}{\left(1+e^{-Z}\right)\left(1+e^{-Y}\right)} \right] - 1 + \lambda_X = 0
\]
\[
    W_B\frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \right] - 1 + \lambda_Y = 0 
\]
\[
    W_B\frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] - 1 + \lambda_Z = 0
\]
\[
  b\left(0\right) \geq0 \hskip.2in b\left(\frac{1}{2}\right) \geq0 \hskip.2in b\left(-\frac{1}{2}\right) \geq0 
\]
\[
  \lambda_X \geq0 \hskip.2in \lambda_Y \geq0 \hskip.2in \lambda_Z \geq0 
\]
\[
  \lambda_X \cdot b\left(0\right) = 0 \hskip.2in \lambda_Y \cdot b\left(-\frac{1}{2}\right) = 0 \hskip.2in \lambda_Z \cdot b\left(\frac{1}{2}\right) = 0 
\]

@@

\subsection{Two Vote Buyers}		
Now we consider the entire game by adding Vote Buyer $A$'s choice of bribes. Vote Buyer A's first order conditions are more complicated because of the dependencies on $\bm a$. Below is the first order condition with respect to $a_0$:
			 \begin{multline}
					 \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left[1+e^{-Y}\right]^2} \frac{\partial b_{-.5}}{\partial a_0} + \\ 
					\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2}\frac{\partial b_{.5}}{\partial a_0} + \\
					\frac{2+e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left[1+e^{-X}\right]^2}\left[1 - \frac{\partial b_0}{\partial a_0} \right] = \frac{1}{W_A}
					\label{eq:focA}
				\end{multline}

Unlike in models with no uncertainty, we do not have knife edge results in which Vote Buyer $A$ uses Vote Buyer $B$'s indifference condition to ensure that he buys no votes--there is no such indifference condition in the presence of uncertainty. However, it's possible that one or both vote buyers will not bribe any legislator because the non-negativity constraints bind for all three bribes. This requires that the willingness-to-pay parameter is sufficiently small.

@@

\begin{proposition}
  It is possible for both vote buyers to bribe legislators on the same vote.
\end{proposition}

>>>>

The Lagrangian for the problem is the same as Expression~\ref{eq:objb}, with the addition of three terms for the non-negativity constraints: $\lambda_X b_0 + \lambda_Y b_{-\frac{1}{2}} + \lambda_Z b_{\frac{1}{2}}$. Thus the full set of first order conditions are
\begin{equation}
    \frac{e^{-X}}{\left(1+e^{-X}\right)^2}\left[\frac{e^{-Z} + e^{-Y}}{\left(1+e^{-Z}\right)\left(1+e^{-Y}\right)} \right] = \frac{1 - \lambda_X}{W_B}
		\label{eq:focB}
\end{equation}
\begin{equation}
    \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \right] = \frac{1 - \lambda_Y}{W_B}
\end{equation}
\begin{equation}
    \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] = \frac{1 - \lambda_Z}{W_B}
\end{equation}
\[
  b\left(0\right) \geq0 \hskip.2in b\left(\frac{1}{2}\right) \geq0 \hskip.2in b\left(-\frac{1}{2}\right) \geq0 
\]
\[
  \lambda_X \geq0 \hskip.2in \lambda_Y \geq0 \hskip.2in \lambda_Z \geq0 
\]
\[
  \lambda_X \cdot b\left(0\right) = 0 \hskip.2in \lambda_Y \cdot b\left(-\frac{1}{2}\right) = 0 \hskip.2in \lambda_Z \cdot b\left(\frac{1}{2}\right) = 0 
\]

@@

\subsection{Two Vote Buyers}		
Now we consider the entire game by adding Vote Buyer $A$'s choice of bribes. Vote Buyer A's first order conditions are more complicated than those of Vote Buyer $B$ because her choices $\bm a$ will impact those of Vote Buyer $B$.

Below is the first order condition with respect to $a_0$, which can be compared to Equation~\ref{eq:focB} for Vote Buyer $B$:
			 \begin{multline}
					 \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left[1+e^{-Y}\right]^2} \frac{\partial b_{-.5}}{\partial a_0} + \\ 
					\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2}\frac{\partial b_{.5}}{\partial a_0} + \\
					\frac{2+e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left[1+e^{-X}\right]^2}\left[1 - \frac{\partial b_0}{\partial a_0} \right] = \frac{1 - \lambda_{XB}}{W_A}
					\label{eq:focA}
				\end{multline}

Unlike in models with no uncertainty, we do not have knife edge results in which Vote Buyer $A$ uses Vote Buyer $B$'s indifference condition to ensure that he buys no votes---there is no such indifference condition in the presence of uncertainty. However, it's possible that one or both vote buyers will not bribe any legislator because the non-negativity constraints bind for all three bribes. This requires that the willingness-to-pay parameters are sufficiently small for both vote buyers.

@@

\begin{proposition}
  It is possible for both vote buyers to bribe legislators on the same vote.
	\label{res:bothbribe}
\end{proposition}
